Deployable Probabilistic Programming

### 2019-04-16 paper/paper.tex
making things look like real

\lstset{ % add your own preferences
    frame=none,
    basicstyle=\footnotesize\ttfamily,
    numbers=left,
    numbersep=5pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}

>>>>

\lstset{ % add your own preferences
    frame=none,
    basicstyle=\ttfamily,
    numbers=left,
    numbersep=5pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}
